Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-31 JCB/main_RNAPyro_JCB.tex
Yet another TODO note
stuff

\documentclass{llncs}
\usepackage[top=1.5in, bottom=1.5in,right=1.5in,left=1.5in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
%\usepackage{jcompbio}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{amsthm} %pour les newtheorem
\usepackage{epstopdf}
\usepackage{xspace}
\usepackage{relsize}
%\usepackage{bbm}
\usepackage{bbold}
\usepackage[numbers]{natbib}
\usepackage[colorinlistoftodos,textsize=small]{todonotes}

@@

\ShowTODO{\setcounter{tocdepth}{1}
\listoftodos} 
\maketitle
%\section{}
%\subsection{}
\begin{abstract}
Analysis of the sequence-structure relationship in RNA molecules are essential to evolutionary studies but also to 
concrete applications such as error-correction methodologies in sequencing technologies. The prohibitive sizes of the
mutational and conformational landscapes combined with the volume of data to proceed require efficient algorithms 
to compute sequence-structure properties. More specifically, here we aim to calculate which mutations increase the most the 
likelihood of a sequence to a given structure and RNA family.\\
In this paper, we introduce \RNApyro, an efficient linear-time and space inside-outside algorithm that computes exact mutational
probabilities under secondary structure and evolutionary constraints given as a multiple sequence alignment with a consensus structure.
We develop a scoring scheme combining classical stacking base pair energies to novel isostericity scales, and apply our techniques
to correct point-wise errors in 5s and 16s rRNA sequences. Our results suggest that \RNApyro is a promising algorithm to complement existing
tools in the NGS error-correction pipeline.

>>>>

\documentclass{llncs}
\usepackage[top=1.5in, bottom=1.5in,right=1.5in,left=1.5in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
%\usepackage{jcompbio}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{amsthm} %pour les newtheorem
\usepackage{epstopdf}
\usepackage{xspace}
\usepackage{relsize}
\usepackage{bbm}
\usepackage[numbers]{natbib}
\usepackage[colorinlistoftodos,textsize=small]{todonotes}

@@

%\ShowTODO{\setcounter{tocdepth}{1}
%\listoftodos} 
\maketitle
%\section{}
%\subsection{}
\begin{abstract}
Analysis of the sequence-structure relationship in RNA molecules are essential to evolutionary studies but also to 
concrete applications such as error-correction methodologies in sequencing technologies. The prohibitive sizes of the
mutational and conformational landscapes combined with the volume of data to proceed require efficient algorithms 
to compute sequence-structure properties. More specifically, here we aim to calculate which mutations increase the most the 
likelihood of a sequence to a given structure and RNA family.\\
In this paper, we introduce \RNApyro, an efficient linear-time and space inside-outside algorithm that computes exact mutational
probabilities under secondary structure and evolutionary constraints given as a multiple sequence alignment with a consensus structure.
We develop a scoring scheme combining classical stacking base pair energies to novel isostericity scales, and apply our techniques
to correct point-wise errors in 5s rRNA sequences. Our results suggest that \RNApyro is a promising algorithm to complement existing
tools in the NGS error-correction pipeline.
